Turbulence in compact to giant HII regions

### 2022-05-17 strucfunc_paper.tex
Start section on nuisance parameters

\subsection{Sanity check on derived values of nuisance parameters}
\label{sec:sanity-check-derived}

@@

At scales larger than \(L/2\),
we see a variety of different shapes for the structure functions
of our sample regions. 
In some cases,
such as Carina and Hubble~X,
\(B(r)\) remains flat at a value of \(\approx 2\sigma^2\),
which is consistent with uncorrelated homogeneous fluctuations
at the largest scales.
For other regions,
such as the Orion Nebula (both inner and outer) and 30~Doradus,
there is a clear downturn in \(B(r)\) at the largest separations.
As discussed above in section~\ref{sec:limit-model-struct},
this is what would be expected if the velocity fluctuations
were inhomogeneous, with a larger amplitude in the center of the map
and a smaller amplitude in the outskirts.
A similar behavior, although not so marked, is shown by
Hubble~V and NGC~595.
The Orion Nebula is a particularly interesting case
since the \(\sigma^2\) derived from the high-resolution dataset of the inner nebula on scales \(\approx \SI{0.1}{pc}\)
is roughly twice as large as that derived from the lower resolution
dataset of the Extended Orion Nebula on scales \(\approx \SI{1}{pc}\)
(compare panels a and b of Figure~\ref{fig:strucfunc-fit-Galactic}).

>>>>

\subsection{On the reasonableness of the derived seeing widths and noise}
\label{sec:sanity-check-derived}
In the model fitting we allow the nuisance observational parameters
\(s_0\) and \(B\noise\) to vary freely within a wide range
(Table~\ref{tab:parameter-ranges}).
This is necessary because of the heterogeneous nature of our source datasets
and the fact that the details of the observational conditions
are not available to us in all cases.
However, it is worthwhile to do perform a sanity check on the values that are implied by our model fits.
To that end, the last column in Table~\ref{tab:Res} gives the FWHM seeing width in arcsec.

@@

At scales larger than \(L/2\),
we see a variety of different shapes for the structure functions
of our sample regions. 
In some cases,
such as Carina and Hubble~X,
\(B(r)\) remains flat at a value of \(\approx 2\sigma^2\),
which is consistent with uncorrelated homogeneous fluctuations
at the largest scales.

For other regions,
such as the Orion Nebula (both inner and outer) and 30~Doradus,
there is a clear downturn in \(B(r)\) at the largest separations.
As discussed above in section~\ref{sec:limit-model-struct},
this is what would be expected if the velocity fluctuations
were inhomogeneous, with a larger amplitude in the center of the map
and a smaller amplitude in the outskirts.
A similar behavior, although not so marked, is shown by
Hubble~V and NGC~595.
The Orion Nebula is a particularly interesting case
since the \(\sigma^2\) derived from the high-resolution dataset of the inner nebula on scales \(\approx \SI{0.1}{pc}\)
is roughly twice as large as that derived from the lower resolution
dataset of the Extended Orion Nebula on scales \(\approx \SI{1}{pc}\)
(compare panels a and b of Figure~\ref{fig:strucfunc-fit-Galactic}).
This is further evidence that the amplitude of velocity fluctuations
increases towards the center of the nebula in this source.

In contrast, other regions,
such as the Lagoon and NGC~346,
show \(B(r)\) increasing at the largest separations,
reaching values significantly larger than \(2\sigma^2\).
This can be evidence for a large-scale linear velocity gradient
across the region (see Figure~13 of \citealp{arthur2016turbulence})
or a periodic fluctuation with \(\lambda > r_0\)
(see section~\ref{sec:limit-model-struct} above).
This latter effect may also explain the behavior of NGC~604,
which shows oscillatory behavior of \(B(r)\),
similar to the light blue line in Figure~\ref{fig:model-strucfunc}b.
